Do More Subdivisions in Wards Increase Turnout? An Analysis of the 2022 Toronto Municipal Election

### 2023-05-31 outputs/paper/paper.qmd
Updated code to count subdivisions by ward

head (cleaned_voter_statistics, 5) |>
 select(ward, sub, percent_voted) |>
  arrange (ward) |>
   kable(
    col.names = c("Ward", "Sub", "Percent Voted"),
  booktabs = TRUE
  )

cleaned_voter_statistics |>
  slice(2:53)

  filter("ward" == 1) |>
  select(ward, sub)

>>>>

head (cleaned_voter_statistics, 5) |>
 select(ward, sub) |>
  arrange (ward) |>
   kable(
    col.names = c("Ward", "Sub"),
  booktabs = TRUE
  )

cleaned_voter_statistics |>
  slice(2:52) |>
  count(
    total = max(sub, na.rm = TRUE)
  )
